Placeholder

### 2021-02-09 Paper_Histograms.Rmd
Stretched out the non white ethnicity figure in the combined retro graph

ggarrange(arranged_retro_ethnicity_non_white,
          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
          nrow = 3,
          common.legend =  TRUE)

ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          common.legend = TRUE,
          ncol = 3,
          nrow = 2)

@@

#Note: Adding the data labels makes the graph look messy

>>>>

#Two columns approach

#ggarrange(arranged_retro_ethnicity_non_white,
#          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
#          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
#          nrow = 3,
#          common.legend =  TRUE)

retro_matrix <- matrix(c(1, 2, 3, 4, 5, 5), nrow = 2, byrow = TRUE)

gridExtra::grid.arrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)

#Three columns approach
#ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
#          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
#          common.legend = TRUE,
#          ncol = 3,
#          nrow = 2)

@@

#Note: Adding the data labels for ethnicity or diagnosis looks messy
